---
title: "Comparison of Datasets by ANOVA"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

The following data is to be assessed as to whether there are significant differences between the individual groups.

```{r, echo =FALSE}
x2 <- x
cf <- format(x2)
cf[is.na(x2)] <- ""
cf
```

This can be displayed in a Boxplot visualisation.  Circles, if present, represent outliers.

```{r, echo=FALSE}
boxplot(x,
        frame = TRUE,
        horizontal = FALSE,
        range = 1, # 1 displays outliers
        las = 0, #horizontal labels
        col = "cornsilk",
        whisklty = 1, # 1 = solid line
        staplelty = 1,# end type, 0 = none
        outpch = 1, # symbol for outliers, 16 = filled circle
        outcol = "black", # colour of outliers
        main = "",
        xlab = "",
        ylab = units)
```





An ANOVA assessment of the data is:

```{r, echo=FALSE}
#convert to a two element stack
xs <- na.omit(stack(x))
# Run ANOVA
anova1 <- aov(values ~ ind, data = xs)
#Review results
summary(anova1)
```
If the "Pr(>F)" value is less than 0.05, it idicates that there is a significant difference between the means of the data sets but doesn't indicate which.  

Looking at the individual differences, using Tukey's HSD criteria, gives an indication of which means differ significantly from each other.  A "p adj" value of less than 0.05 indicates a  significant difference.

```{r,echo=FALSE}
TukeyHSD(anova1)
```

