---
title: "Control Chart Review"
output: word_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo=FALSE,message=FALSE}


colnames(x)[1] <- "SAMPLE_NUMBER"
library(dplyr)
library(psych)
library(ggplot2)

testname <- substr(x$ANALYSIS[1],1,6)

Name <- x$REPORTED_NAME[1]
Units <- tolower(sub("_P_","/",(x$REPORTED_UNITS[1])))
testcode <- paste("Test Code :", testname)
```
###`r testcode`

```{r echo=FALSE}
# Input parameters ----------------------------------------------------------------

max.pts <- max.pts # Maximum points plotted
points <- points   # How many points used to set control lines

# ---------------------------------------------------------------------------------
```

The recent control samples with this test have been:

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# Clean the data
data.in <- select(x, everything())%>%
        arrange(SAMPLE_NUMBER)%>%
        select(ASSIGNED_OPERATOR, SAMPLING_POINT, ENTRY)%>%
        mutate(ENTRY = as.numeric(as.character(ENTRY)))%>%
        na.omit


boxplot(data.in$ENTRY~data.in$SAMPLING_POINT,
         main = paste("Comparative ",testname," SRM/IRM Results"),
        ylab = paste(Name," ", Units))
```

The following is the most recent control chart (control lines caluclated after omitting any outliers (shown in red)).

This chart uses up to the `r max.pts` most recent data points (less if there are not that many points available) and sets the control lines using the first `r points` of them.  If present, green points represent 'one side of the mean' trending error and yellow points represent a 'seven point' increasing or decreasing trend.

```{r, echo=FALSE,message=FALSE}
j <- length(unique(data.in$SAMPLING_POINT))

remove.outliers <- function(x, na.rm = TRUE, ...) {
        qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
        H <- 1.5 * IQR(x, na.rm = na.rm)
        y <- x
        y[x < (qnt[1] - H)] <- NA
        y[x > (qnt[2] + H)] <- NA
        y
}
srm1 <- unique(data.in[2])

srm <- srm1[j,]

data.in3 <- data.in[data.in$SAMPLING_POINT==srm,]
names(data.in3) <- c("Operator", "SRM","A")
data.in3 <- select(data.in3, everything())%>%
        filter( between(row_number(), n()-max.pts, n()))

clean <- remove.outliers(data.in3$A[1:points])
xx <- describe(clean)

UCL <- xx$mean + 3*xx$sd
UWL <- xx$mean + 2*xx$sd
Centre <- xx$mean 
LWL <- xx$mean - 2*xx$sd
LCL <- xx$mean - 3*xx$sd
MU <- 2*xx$sd

CC <- c(UCL, UWL, Centre, LWL, LCL ,MU)
Labels <- c("UCL", "UWL", "Centre", "LWL", "LCL", "MU +/-")
Clines <- cbind(Labels, round(CC,3))
Clines <- as.data.frame(Clines)

# Calculate outliers -----------------------------------------------------------
data.in3$outliers = NA
j <- nrow(data.in3)

for (i in 1:j) {
        if(between(data.in3$A[i], LCL, UCL)==TRUE)
           data.in3$outliers[i]=data.in3$A[i]
}

# Calculate trend on one side of mean ------------------------------------------
data.in3$T1 <- 1
data.in3$T2 <- 1

for (i in 2:j) {
        if(data.in3$A[i] < Centre)
                data.in3$T1[i] = -1
}
n=1
for (i in 2:j) {
        if(data.in3$T1[i] == data.in3$T1[i - 1]) {
                data.in3$T2[i] = n +1
                n = n + 1
        } else {  
                data.in3$T2[i] = 1
                n = 1
        }
}

data.in3$T3 <- NA
for (i in 1:j) {
        if(data.in3$T2[i] > 6)
                data.in3$T3[i] = data.in3$A[i]
}

# Trending up or down -----------------------------------------------------

data.in3$T4 <- 1
data.in3$T5 <- 1

for (i in 2:j) {
        if(data.in3$A[i] < data.in3$A[i-1])
                data.in3$T4[i] = -1
}
n=1
for (i in 2:j) {
        if(data.in3$T4[i] == data.in3$T4[i - 1]) {
                data.in3$T5[i] = n +1
                n = n + 1
        } else {  
                data.in3$T5[i] = 1
                n = 1
        }
}

data.in3$T6 <- NA
for (i in 1:j) {
        if(data.in3$T5[i] > 6)
                data.in3$T6[i] = data.in3$A[i]
}


# Plotting ----------------------------------------------------------------

plot(data.in3$A, 
        type="p", 
        pch= 19, 
        cex=1.0, 
        col ="red", 
        ylim = c(LCL*0.9,UCL*1.1),
        ylab = paste(Name," ", Units),
        xlab="")

par(new=T)

plot(data.in3$outliers, 
        type="o", 
        pch=19, 
        cex=1.0, 
        col="grey40", 
        ylim = c(LCL*0.9,UCL*1.1), 
        ylab = paste(Name," ", Units), 
        main = paste(srm, "(", Name,") Control Chart"),
        xlab="")

par(new=T)

plot(data.in3$T3, 
     type="p", 
     pch= 19, 
     cex=1.0, 
     col ="limegreen", 
     ylim = c(LCL*0.9,UCL*1.1),
     ylab = paste(Name," ", Units),
     xlab="")

par(new=T)

plot(data.in3$T6, 
     type="p", 
     pch= 19, 
     cex=1.0, 
     col ="orange", 
     ylim = c(LCL*0.9,UCL*1.1),
     ylab = paste(Name," ", Units),
     xlab="")

abline(h=Centre, col = "blue", lty=2, lwd=2)
abline(h=UCL, col = "red", lty=2, lwd=2)
abline(h=UWL, col = "darkgreen", lty=3, lwd=2)
abline(h=LWL, col = "darkgreen", lty=3, lwd=2)
abline(h=LCL, col = "red", lty=2, lwd=2)

```

The histogram of the data points.  Red line = mean:

```{r, echo=FALSE}
hist(data.in3$outliers, 
     breaks=20, 
     xlab=srm,
     main = paste("Control Chart",srm,"data distribution"))
abline(v = Centre, col = "red", lty = 2)
```

**Review**
1. Is it skewed?
2. Is it normal shaped?
.

The general statistics for the data are:

```{r,echo=FALSE}
print(describe(clean))
```

The values for the control lines used  in the chart are:

```{r, echo=FALSE}
print (Clines)
```

The results obtained by each operator.  Blue line = mean:

```{r, echo=FALSE}
xx <- boxplot(data.in3$A~data.in3$Operator, las=2, cex.axis = 0.8)
abline(h=Centre, col = "blue", lty=2, lwd=2)
```

Number of control samples run by each operator:

```{r, echo=FALSE}
table(data.in3$Operator)
```



